---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# biosampleR

<!-- badges: start -->
<!-- badges: end -->

The goal of biosampleR is to provide a simple set of functions to generate common biodiversity
measures from count data, along with confidence intervals around these measures using bootstrapping.
The package also provides functions to assess the effect of sampling effort on the precision of 
these measures.

## Installation

You can install the development version of biosampleR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("csim063/biosampleR")
```

Or you can install the stable version of biosampleR from [CRAN](https://cran.r-project.org/) with:

``` r
install.packages("biosampleR")
```

## Example

The the functions in the package may be used in a single workflow as follows:

```{r example}
library(biosampleR)

# Import count data
df <- BCI #Using the BCI dataset from the vegan package as an example

# Calculate biodiversity measures with confidence intervals
# (both per site and overall for all sites)
stats <- get_sample_stats(df)

# Generate subsamples of a data frame with a number of sites between a minimum
# and maximum value.
ss <- generate_subsamples(df,
                          min_sites = 1,
                          max_sites = 5,
                          step = 1,
                          reps = 2)

# Calculate change in variance of biodiversity measures with increasing sampling effort
data  <- unlist(ss, recursive = FALSE)
data <- do.call(rbind, data)

calc_delta_var(data,
              col_name = "richness",
            site_name = "num_sites",
          rep_name = "rep",
        visualize = TRUE)
```

## Code of Conduct

Please note that the **spectre** package is released with a Contributor
Code of Conduct. By contributing to this project,
you agree to abide by its terms.

To see how to contribute to this project, please see the Contributing
guidelines.